RadLib: a radiative property model library for CFD

### 2021-09-15 manuscript/manuscript.tex
Rolling back purely stylistic edits. Finished edits to remainder of paper. Added section to reviewer response document with summary of revisions made.

        \begin{abstract}
            RadLib is a C++ library of radiation property models that can be applied to a variety of systems involving
            radiative heat transfer, including CFD simulations. RadLib includes three major radiation property
            models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the
            rank-correlation spectral line-weighted-sum-of-gray-gases (RCSLW) model. RadLib includes C++, Python, and
            Fortran interfaces and can be expanded to include additional models. Several example cases illustrate the
            use of the models with an included ray-tracing solver, compare their accuracy relative to
            line-by-line (LBL) solutions, and compare their computational costs. Finally, RadLib is coupled with Fire
            Dynamics Simulator (FDS) in an ethylene burner flame example case to demonstrate its use with existing
            CFD software. RadLib provides researchers with convenient access to validated radiation property models
            and a framework for further development.
        \end{abstract}

@@

    \begin{small}
        \noindent
        {\em Program Title:} RadLib                                         \\
        {\em CPC Library link to program files:} (to be added by Technical Editor) \\
        {\em Developer's repository link:} https://github.com/BYUignite/radlib \\
        {\em Code Ocean capsule:} https://codeocean.com/capsule/0997975/tree \\
        {\em Licensing provisions(please choose one):} MIT \\
        {\em Programming language:} C++, Fortran, Python \\
        {\em Nature of problem(approx. 50-250 words):} \\
        Radiative heat transfer in combustion CFD problems is typically neglected or oversimplified, resulting in
        significant error and inaccuracy in combustion simulations. Radiation modeling, however, often requires a
        high degree of specialization due to its complexity and the challenges associated with implementation in
        existing CFD codes, which presents a substantial obstacle to researchers who wish to address the inaccuracies
        introduced by insufficient radiative heat transfer modeling in combustion simulations. \\
        {\em Solution method(approx. 50-250 words):}\\
        We present RadLib, an open-source C++ library of validated radiation property models that can be applied
        alongside various RTE solution methods to ease some of the obstacles associated with radiation modeling for
        combustion CFD. The package includes C++, Fortran, and Python interfaces, several illustrative examples with
        a provided ray-tracing solver, and an integrated example using Fire Dynamics Simulator (FDS). RadLib can also
        be expanded to include additional radiative property models and interfaces. \\
        {\em Additional comments including restrictions and unusual features (approx. 50-250 words):}\\
        The RadLib library is intended to be used in Linux-like terminal applications.
        \\

@@

    Modeling radiative heat transfer in high temperature participating media systems is challenging, particularly in
    combustion systems.
    Combustion CFD is uniquely challenging because
    it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and
    radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction
    kinetics---that span many orders of magnitude in both length and time scales.
    Radiation modeling often complicates combustion simulations because accurate models can be difficult to
    implement and
    computationally expensive relative to overall simulation costs.
    Radiative heat transfer modeling in combustion systems
    is frequently neglected or oversimplified, resulting in significant flame temperature prediction errors~\citep{Modest_2016}.
    Additionally, some late-stage flame phenomena, particularly soot behavior and flame sheet breakthrough,
    increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate
    accurately without robust radiation modeling~\cite{Modest_2013}. These problems motivated development of the
    RadLib library, which implements three radiation property models with C++, Python, and Fortran interfaces and
    provides a framework for additional models and further development, providing researchers with convenient access to
    advanced radiation property modeling tools.

    The core mechanisms of radiative phenomena are physically and mathematically complex. Unlike other modes of heat
    transfer, radiation is governed by a set of directionally and spectrally dependent integro-differential equations
    known as the radiative transfer
    equations (RTEs). Computational radiation solvers require two distinct
    but interconnected parts: (1) a solution approach for the radiative transfer equations (RTEs) and (2) a radiative
    property model.
    The complexity, implementation, and computational costs of these two parts can vary widely depending on the models
    chosen. For example, the optically thin approximation for solution of the RTE is trivial, while the discrete
    ordinates model (DOM) and
    reverse Monte Carlo ray tracing (RMCRC) model, among others, are significantly more involved. Similarly,
    radiation property models range from simple correlations for computing mean absorption coefficients to gray gas
    models, including the weighted sum of gray gases (WSGG) model, to more advanced spectral
    line-weighted-sum-of-gray-gases (SLW) models to full line-by-line (LBL) treatment.
    In practical engineering simulations, solving the RTE is
    often the most complex and costly part of radiative simulation, but advanced property models such as the
    rank-correlated SLW (RCSLW) model, discussed in Section~\ref{s:RCSLW}, are nontrivial to understand, implement, and
    validate.
    RadLib addresses this second radiative property model part of radiation simulation by providing a set of
    implemented and validated radiation property models that can be applied to various solution approaches for the RTE.

    Consider an absorbing, emitting, and non-scattering medium. The RTE describes the radiative intensity $I$ at a
    specified wavenumber $\eta$ in unit direction $\mathbf{s}$ as
% 
    \begin{linenomath}
        \begin{equation}
            \label{e:RTE_general}
            \frac{dI_{\eta}}{ds} = -\kappa_{\eta}I_{\eta} + \kappa_{\eta}I_{b,\eta},
        \end{equation}
    \end{linenomath}
%
    where $I_{\eta}$ is the spectral radiative intensity, $I_{b,\eta}$ is the blackbody spectral radiative intensity
    (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length
    along direction $\mathbf{s}$. Solving the RTE requires information about the radiative properties of the
    materials and media in the system. Radiative property data typically takes the form of radiation absorption
    coefficients $\kappa$, which are provided by a radiation property model.
    Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules and depend
    on the local thermochemical state of the system (e.g., temperature, pressure, and composition).
    Radiation property models typically consist of correlations between radiative properties and high-resolution
    spectral databases, reducing the huge amount of spectral data and
    simplifying evaluation of radiation absorption coefficients~\cite{Zhang_2002b}.

    The direct solution of the spectral RTE using so-called line-by-line (LBL) calculations---in which the RTE is solved
    for each individual spectral line---is computationally prohibitive for most practical configurations and used
    primarily for model validation. In contrast, simple ``band'' models rely on estimated or averaged ``line-of-sight''
    property values that cannot be directly incorporated into the RTE solution.
    Modern band models, which require access to high-resolution spectral databases, tend to reorder spectral emission
    levels rather than averaging across sequential absorption bands, but these can lose accuracy when applied to
    nonhomogeneous media and may still require large numbers of RTE evaluations~\citep{Modest_2016}.

    Global models are an important class of radiation property models that use spectrally-integrated radiation
    properties~\cite{Hottel_1967,Modest_2013,Modest_2016}. Assuming spectrally uniform (gray) properties over a
    wavenumber region $j$, we can integrate Eq.~\ref{e:RTE_general} over a set of fixed wavenumber ranges $\eta_j$ to
    obtain
%
    \begin{linenomath}
        \begin{equation}
            \label{e:RTE_wsgg}
            \frac{dI_j}{ds} = -\kappa_jI_j + a_j\kappa_jI_b, \hspace{20pt} j=0,1,...,n,
        \end{equation}
    \end{linenomath}
%
    where $I_b$ is the total blackbody intensity, $I_j$ is the total radiative intensity in the region defined by gray
    gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
%
    \begin{linenomath}
        \begin{align}
            &a_j= \frac{\int_{\eta_j}I_{b,\eta}d\eta}{I_b},\\
            &\sum_j a_j = 1.
        \end{align}
    \end{linenomath}
%
    Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be evaluated for each of the $n$ gray
    gases. Normally, an additional ``clear gas'', $j=0$, is included to represent transparent windows in the
    spectrum for which $\kappa_0=0$. This gray gas approach allows calculation of the total radiative intensity $I$
    by summing the individual gray gas intensities:
%
    \begin{linenomath}
        \begin{equation}
            I=\int_{\eta=0}^{\infty}I_{\eta}d\eta=\sum_{j=1}^n I_j.
        \end{equation}
    \end{linenomath}
%
    The heat flux $\mathbf{q}$ (kW/m$^2$) can be calculated by integrating over the directional solid
    angles $\mathbf{s}\Omega$ on the sphere, and the volumetric radiative heat source $Q$ (kW/m$^3$) can be found by
    computing the divergence of the resulting vector field:
%
    \begin{linenomath}
        \begin{equation}
            \mathbf{q} = \int_{4\pi}I(\mathbf{s})\mathbf{s}d\Omega,
        \end{equation}
    \end{linenomath}
%
    \begin{linenomath}
        \begin{equation}
            Q = -\nabla\cdot\mathbf{q}.
        \end{equation}
    \end{linenomath}
%
    Global models are especially attractive in computational heat transfer applications because they can provide good accuracy
    while limiting computational costs.

@@

    At present, RadLib includes three radiation property models of varying complexity: the Planck Mean (PM) absorption
    coefficients model, a weighted sum of gray gases (WSGG)
    model, and the rank-correlated spectral line-weighted-sum-of-gray-gases (RCSLW) model. These models were chosen
    for their relevance to practical radiative heat transfer simulations. They represent increasing levels of complexity, computational cost, and accuracy. Each model is discussed in more detail in the following sections.

    Radiation absorption coefficients are typically calculated via correlations developed from high-resolution
    spectral databases like RADCAL, HITRAN, and HITEMP~\citep{Grosshandler_1993,Rothman_2010} that relate spectral line strength to properties such as temperature, pressure, and gas composition \citep{Zhang_2002b}. At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$), depending on the model, and soot. The property models implemented in RadLib apply only to non-scattering media.
    Table~\ref{t:models} summarizes RadLib's three radiative property models and the thermodynamic conditions under
    which they apply.

    \begin{table}
        \caption{Summary of radiative property models in RadLib and the range of conditions under which they can be
        applied.}
        \label{t:models}
        \centering
        \resizebox{\textwidth}{!}{
            \begin{tabular}{l l l l l}
                \hline
                Model & T range & P range & Gas species & Refs.   \\
                \hline
                PM    & 300\textendash 2500 K & 1 atm & \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4} & \cite{TNF} \\
                WSGG  & 300\textendash 2400 K & 1 atm & \ce{CO2}, \ce{H2O} & \cite{Bordbar_2014,Bordbar_2020} \\
                RCSLW & 300\textendash 3000 K & 0.1\textendash 50 atm & \ce{CO2}, \ce{H2O}, \ce{CO} & \cite{Solovjov_2017} \\
                \hline
            \end{tabular}
        }
    \end{table}

@@

    The Planck Mean (PM) model is the simplest of the three models implemented. This model assumes a single gray gas
    (with no transparent gas)
    and computes the absorption coefficient as a function of temperature and gas composition.

    The particular version of the model implemented comes from the Turbulent Nonpremixed Flames (TNF)
    workshop~\cite{TNF}, a long-running collaboration between experimental and computational researchers in turbulent
    combustion~\citep{Smith_2003,Barlow_2001}. The workshop includes a number of laboratory jet flames that have been
    extensively characterized---including temperature, velocity, and composition profiles---and which serve as target
    flames for computational scientists validating simulations and models. The PM model implemented in RadLib is the
    one recommended by the TNF workshop and is widely used in turbulent combustion simulation research.

    For each gas species considered, the PM model provides the absorption coefficient $\kappa(T)$ as a fourth or fifth order
    polynomial fit in one of two temperature ranges to values computed from the RADCAL spetral database~\cite{Grosshandler_1993}.
    It considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, and \ce{CH4} at temperatures between 300 K and 2500 K.
    \ce{CO} and \ce{CH4} contribute significantly less to radiative absorption and emission than \ce{CO2} and
    \ce{H2O} do, but are included here because of their strong presence in the TNF workshop flames, several of which
    use methane (\ce{CH4}) or syngas (mixture of \ce{CO} and \ce{H2}) fuels. For more details on the TNF workshop
    flames and the TNF radiation model, see \cite{TNF}.

    The PM model is not as accurate as the other two models considered; this is illustrated by the examples cases
    presented in Sections~\ref{s:Examples} and~\ref{s:discussion}.
    It is implemented in RadLib primarily for comparison and evaluation against other radiation property models
    because it is commonly used in combustion simulations.
    The model has been reported to overpredict radiative losses and underpredict flame temperature by as much as 100
    K or more~\cite{Frank_2000,Zhu_2002,Coelho_2002}, though this depends strongly on the simulation geometry. Accurate
    results have been reported for hydrogen jet flames~\cite{Barlow_1999}.

    The PM model is most often used in conjunction with the optically-thin approximation for solving the RTE; in this
    case, the radiative source term of the energy transport equation is particularly simple, and the overall
    computational cost of the radiative treatment is negligible compared to other aspects of reacting flow
    simulations. Many combustion applications with relatively low radiative heat loss can be considered optically
    thin with respect to radiation; non-sooting laboratory-scale research jet flames, for example, tend to experience
    radiative losses of about 5\%. In such cases, when radiative losses are relatively small, the accuracy of the
    radiative property model is not as crucial to simulation results, and simpler radiative treatments like the PM model
    may be appropriate.

@@

    Weighted sum of gray gases (WSGG) models generate radiation absorption coefficients for use with the spectrally
    integrated RTE (Eq.~\ref{e:RTE_wsgg}).
    RadLib implements the WSGG model presented by Bordbar et al.~\citep{Bordbar_2014,Bordbar_2020}. This model
    computes emissivity for varying gas temperature, mixture composition, and path length using the HITEMP 2010
    database~\cite{Rothman_2010}. The $k_j$ and $a_j$ values are correlated to these results using polynomial fits as
    summarized below. The model considers mixtures of gaseous \ce{CO2} and \ce{H2O}, the two most significant
    radiatively participating species in most combustion environments, using four gray gases and one clear gas.
    Absorption coefficients are calculated by
%
    \begin{linenomath}
        \begin{equation}
            \kappa_j=\sum_{k=0}^{4}d_{j,k}M_r^k,
        \end{equation}
    \end{linenomath}
%
    where $\kappa_j$ is the absorption coefficient for gray gas $j$, $d_{j,k}$ is a correlated model coefficient, and
    $M_r$ is the molar ratio $x_{\mathrm{H_2O}}/x_{\mathrm{CO_2}}$. The weight factors are calculated by
%
    \begin{linenomath}
        \begin{equation}
            a_j=\sum_{k=0}^{4}b_{j,k}T_r^k,
        \end{equation}
    \end{linenomath}
%
    where $a_j$ is the weighting factor for gas $j$, $b_{i,j}$ is computed as shown below,  and $T_r$ is a scaled
    temperature equal to $T/T_{ref}$ with $T_{ref}$=1200 K. The value of $b_{i,j}$ is calculated by
%
    \begin{linenomath}
        \begin{equation}
            b_{j,k}=\sum_{i=0}^{4}C_{j,k,i}M_r^i,
        \end{equation}
    \end{linenomath}
%
    where $C_{j,k,i}$ is a correlated model coefficient. The model coefficients $d_{j,k}$ and $C_{j,k,i}$ are
    provided by Bordbar~et~al.~\citep{Bordbar_2014,Bordbar_2020}; RadLib uses updated values
    in~\cite{Bordbar_2020}. The model is valid for temperatures between 300 K and 2400 K; temperatures outside this range use the value at the respective bound.

    This particular WSGG model was chosen for RadLib for its performance, accuracy, and flexibility. Most WSGG models
    are limited to specific values of the molar \ce{H2O}--\ce{CO2} ratio, or to a limited range of values. This is
    true of Bordbar et al.'s 2014 model~\cite{Bordbar_2014}, which used correlations valid for $0.01\le M_r\le4$.
    That paper summarizes a number of WSGG models and gives the applicable molar ratio range for several recent WSGG
    model versions.
    Bordbar et al.~\citep{Bordbar_2020} extended the molar ratio range to arbitrary values of $M_r$ by interpolating
    $\kappa_j$ and $a_j$ between the pure component values and the corresponding limit on $M_r$ for values outside of
    the correlated range. RadLib implements this extended version of the model.

@@

    SLW and WSGG models are similar in that they approximate real gas mixtures with a set of radiatively gray gases,
    but differ in the way that the gray gases are constructed. In traditional WSGG models, the component gases are only
    conceptually gray, and the absorption coefficients and weights are determined empirically \citep{Badger_2019}. In SLW approaches, however, the gases are gray in a given spectral band by construction. Rather than defining a gray gas $j$ by integrating over a band of sequential wavenumbers $\eta$ (which may have highly variable absorption coefficients), SLW models define a gray gas $j$ by integrating over a set of nonsequential wavenumbers that correspond to a given band of the absorption cross section $C_{\eta}$ with values constant to within the width of the band.

@@

    In the PM model, which treats a gas mixture as a single gray gas, the soot absorption coefficient
    calculated from Eq.~\ref{e:soot2} is simply added to the gas absorption coefficient. Using the given values of $C_0$ and $C_2$ above, the expression for the soot absorption coefficient simplifies to  $\kappa_s=1817f_vT$ with units of \si{m^{-1}}.

@@

    These cases are intended to illustrate the use of the RadLib library and are not exhaustive. Details about these examples and their motivations can be found in their respective references. Comparison of these results to the LBL data, shown here, serve as model validation. For WSGG and RCSLW, direct comparison (not shown) of RadLib was made to examples presented in the model references with identical results (up to the resolution of the available data), which serves as verification of the implementation.

@@

\bibitem{Modest_2013}
M.~F. Modest, {Radiative Heat Transfer}, third edition Edition, {Academic
Press}, New York, 2013.

>>>>

        \begin{abstract}
            RadLib is a C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations. RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model. RadLib includes C++, Python, and Fortran interfaces and can be expanded to include additional models.Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions. A CFD example is provided of an ethylene burner in a compartment using Fire Dynamics Simulator (FDS). The computational cost of the models is compared. RadLib provides researchers with convenient access to validated radiation property models and a framework for further development.
        \end{abstract}

@@

    \begin{small}
        \noindent
        {\em Program Title:} RadLib                                         \\
        {\em CPC Library link to program files:} (to be added by Technical Editor) \\
        {\em Developer's repository link:} https://github.com/BYUignite/radlib \\
        {\em Code Ocean capsule:} https://codeocean.com/capsule/0997975/tree \\
        {\em Licensing provisions(please choose one):} MIT \\
        {\em Programming language:} C++, Fortran, Python \\
        {\em Nature of problem(approx. 50-250 words):} \\
        Radiative heat transfer in combustion CFD problems is typically neglected or oversimplified, resulting in significant error and inaccuracy in combustion simulations. Radiation modeling, however, often requires a high degree of specialization due to its complexity and the challenges associated with implementation in existing CFD codes, which presents a substantial obstacle to researchers who wish to address the inaccuracies introduced by insufficient radiative heat transfer modeling in combustion simulations. \\
        {\em Solution method(approx. 50-250 words):}\\
        We present RadLib, an open-source C++ library of validated radiation property models that can be applied
        alongside various RTE solution methods to ease some of the obstacles associated with radiation modeling for
        combustion CFD. The package includes C++, Fortran, and Python interfaces, several illustrative examples with
        a provided ray-tracing solver and an integrated example using Fire Dynamics Simulator (FDS).
        RadLib can also be expanded to include additional radiation property models and interfaces.\\
        {\em Additional comments including restrictions and unusual features (approx. 50-250 words):}\\
        The library is intended to be used in Linux-like terminal applications.
        \\

@@

    Modeling radiative heat transfer in participating media in high temperature systems is a challenging problem.
    Combustion is one of the key radiative transfer applications, and combustion CFD is uniquely challenging because
    it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and
    radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction
    kinetics---that span many orders of magnitude in both length and time scales. Combustion simulations are often
    complicated by a lack of accurate radiation modeling, which can be difficult to implement and computationally
    expensive relative to overall simulation cost. Frequently, radiative heat transfer modeling in combustion systems
    is either neglected or oversimplified, resulting in significant errors flame temperatures~\citep{Modest_2016}.
    Additionally, some late-stage flame phenomena, particularly soot behavior and flame sheet breakthrough,
    increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate
    accurately without robust radiation modeling \cite{Modest_2013}. These problems motivated development of the
    RadLib library, which implements three radiation property models with C++, Python, and Fortran interfaces and
    provides a framework for additional models and further development, giving researchers convenient access to
    advanced radiation property modeling tools.

    The core mechanisms of radiative phenomena are physically and mathematically complex. Unlike other modes of heat
    transfer, radiation is governed by a set of integro-differential equations that depend on both direction and
    wavelength, known as the radiative transfer equations (RTE). Computational radiation solvers require two distinct
    but interconnected parts: (1) a solution approach for the radiative transfer equations (RTE) and (2) a radiative
    property model.
    Complexity, implementation, and computational cost of these two parts can vary widely depending on the models
    chosen. The optically thin model for solution of the RTE is trivial, while the discrete ordinates model (DOM) and
    reverse Monte Carlo ray tracing (RMCRC) model, among others, are significantly more involved. Similarly, radiation
    property models range from simple correlations for computing mean absorption coefficients to gray gas models, including the weighted
    sum of gray gases (WSGG) model, to more advanced spectral line-weighted-sum-of-gray-gases (SLW) models to full
    line-by-line (LBL) treatment. In practical engineering simulations, the solution of the RTE is
    often the most complex and costly part of radiative simulation, but advanced property models such as the Rank
    Correlated SLW (RCSLW), discussed here, are nontrivial models to understand, implement, and validate.
    RadLib addresses this second radiative property model part of radiation simulation by providing a set of
    implemented and validated radiation property models that can be applied to various solution approaches for the RTE.

    For an absorbing, emitting, and non-scattering medium (considered here), the RTE for intensity $I$ at a specified wavenumber $\eta$ in unit direction $\mathbf{s}$ is described by
% 
    \begin{linenomath}
        \begin{equation}
            \label{e:RTE_general}
            \frac{dI_{\eta}}{ds} = -\kappa_{\eta}I_{\eta} + \kappa_{\eta}I_{b,\eta},
        \end{equation}
    \end{linenomath}
%
    where $I_{\eta}$ is the radiative spectral intensity, $I_{b,\eta}$ is the spectral blackbody radiative intensity
    (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length
    along direction $\mathbf{s}$.
    Solving the RTE requires information about the radiative properties of the materials and media in the system.
    Radiative property data typically takes the form of radiation absorption
    coefficients $\kappa$, which are provided by a radiation property model.
    Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical
    energy levels of gas molecules and depend
    on the local thermochemical state of the system (e.g., temperature, pressure, and composition).
    Radiation property models typically consist of correlations between radiative properties and high-resolution
    spectral databases, reducing the huge amount of spectral data and
    simplifying evaluation of radiation absorption coefficients \cite{Zhang_2002b}.

    The direct solution of the spectral RTE using so-called line-by-line calculations, in which the RTE is solved for
    each
    individual spectral line, is computationally prohibitive for most practical configurations and is used primarily
    for model
    validation. Some band models rely on estimated or averaged "line-of-sight" property values that cannot be directly
    incorporated into the RTE. Modern band models require high-resolution databases and reorder emission levels rather than averaging across sequential
    absorption bands, but these can lose accuracy when applied to nonhomogeneous media and may still require large numbers of
    RTE evaluations \citep{Modest_2016}.

    Global models are an important class of radiation property models that use spectrally-integrated radiation properties \cite{Hottel_1967,Modest_2013,Modest_2016}. Assuming spectrally uniform (gray) properties over a wavenumber region $j$, we can integrate Eq.~\ref{e:RTE_general} over the fixed wavenumber ranges $\eta_j$ to obtain
%
    \begin{linenomath}
        \begin{equation}
            \label{e:RTE_wsgg}
            \frac{dI_j}{ds} = -\kappa_jI_j + a_j\kappa_jI_b, \hspace{20pt} j=0,1,...,n,
        \end{equation}
    \end{linenomath}
%
    where $I_b$ is the blackbody intensity, $I_j$ is the radiative intensity in the region defined by gray gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
%
    \begin{linenomath}
        \begin{align}
            &a_j= \frac{\int_{\eta_j}I_{b,\eta}d\eta}{I_b},\\
            &\sum_j a_j = 1.
        \end{align}
    \end{linenomath}
%
    Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be evaluated for each of the $n$ gray gases. Normally, an additional ``clear gas'', $j=0$, is included that represents transparent windows in the spectrum for which $\kappa_0=0$. This gray gas approach allows calculation of the total radiative intensity $I$ by summing the individual gray gas:
%
    \begin{linenomath}
        \begin{equation}
            I=\int_{\eta=0}^{\infty}I_{\eta}d\eta=\sum_{j=1}^n I_j.
        \end{equation}
    \end{linenomath}
%

    The heat flux $\mathbf{q}$ (in units of kW/m$^2$) and volumetric radiative heat source $Q$ (kW/m$^3$) can be calculated by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere and finding the divergence of the resulting vector field,
%
    \begin{linenomath}
        \begin{equation}
            \mathbf{q} = \int_{4\pi}I(\mathbf{s})\mathbf{s}d\Omega.
        \end{equation}
    \end{linenomath}
%
    \begin{linenomath}
        \begin{equation}
            Q = -\nabla\cdot\mathbf{q}.
        \end{equation}
    \end{linenomath}
%
    Global models are especially attractive in computational heat transfer applications because they can provide good accuracy
    while limiting computational costs.

@@

    At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption
    coefficients, most often applied alongside the optically thin approximation, a weighted sum of gray gases (WSGG)
    model, and the rank-correlated spectral line-weighted-sum-of-gray-gases (RCSLW) model. These models were chosen
    for their relevance to practical radiative heat transfer simulations. They represent increasing levels of complexity, computational cost, and accuracy. Each model is discussed in more detail in the following sections.

    Radiation absorption coefficients are typically calculated via correlations developed from high-resolution spectral databases like RADCAL, HITRAN, and HITEMP \citep{Grosshandler_1993,Rothman_2010} that relate spectral line strength to properties such as temperature, pressure, and gas composition \citep{Zhang_2002b}. At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$), depending on the model, and soot. The property models implemented in RadLib apply only to non-scattering media.
    Table~\ref{t:models} summarizes RadLib's three radiative property models and the thermodynamic conditions under
    which they apply.

    \begin{table}
        \caption{Summary of radiative property models in RadLib.}
        \label{t:models}
        \centering
        \resizebox{\textwidth}{!}{
            \begin{tabular}{l l l l l}
                \hline
                Model & T range (K) & P range (atm) & Gas species & Refs.   \\
                \hline
                PM      & 300\textendash 2500 & 1                 & \ce{H2O}, \ce{CO2}, \ce{CO}, \ce{CH4}  &
                \cite{TNF} \\
                WSGG    & 300\textendash 2400 & 1                 & \ce{H2O}, \ce{CO2} & \cite{Bordbar_2020,
                    Bordbar_2014} \\
                RCSLW   & 300\textendash 3000 & 0.1\textendash 50 & \ce{H2O}, \ce{CO2}, \ce{CO} &
                \cite{Solovjov_2017} \\
                \hline
            \end{tabular}
        }
    \end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    The Planck Mean (PM) model is the simplest of the three models implemented. This model assumes a single gray gas
    (with no transparent gas)
    and computes the absorption coefficient as a function of temperature, pressure, and gas composition.

    The particular version of the model implemented is from the Turbulent Nonpremixed Flames (TNF) workshop \cite{TNF}. This is a long-running collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}. The workshop includes a number of laboratory jet flames that have been extensively researched for flame temperature, velocity, and composition profiles, and these serve as target flames for computational scientists to validate simulations and models. The PM model implemented here is the one advocated (and hence widely used) by the TNF workshop.

    For each species, the PM model provides the absorption coefficient as a fourth or fifth order polynomial fit in one
    of two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
    Ultimately, the model accommodates temperatures between 300 K and 2500 K. See
    \cite{TNF} for details and references. The PM model here considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
    The last two species have lower absorption than the first two, but are included because \ce{CH4} and syngas
    (consisting of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in the TNF flames
    in high concentrations in the fuel stream. (\ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.)

    The PM model is not as accurate as the other two models considered, and this is illustrated in Section~\ref{s:discussion}.
    It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its relatively common use in some simulations.
    The model has been reported to overpredict radiative losses and underpredict flame temperature by as much as 100 K or more \cite{Frank_2000,Zhu_2002,Coelho_2002}, though this will depend strongly on the geometric configuration. Accurate results have been reported for hydrogen jet flames \cite{Barlow_1999}.

    The PM model is often used in conjunction with the optically-thin approximation for solving the RTE, in which case the radiative source term of the energy transport equation is particularly simple, and the overall computational cost of the radiative treatment is negligible in comparison to other aspects of a reacting flow simulation. Many smaller combustion applications are radiatively thin, and have smaller radiative heat loss. It is not uncommon for non-sooting laboratory-scale research jet flames to have radiative losses of around 5\%. At these levels, the accuracy of the radiative property model is not as crucial, and simpler models like the PM model are appropriate.

@@

    Weighted sum of gray gases (WSGG) models generate radiation absorption coefficients for use with the spectrally integrated RTE (Eq.~\ref{e:RTE_wsgg}).
    RadLib implements the WSGG model presented by Bordbar et al. \citep{Bordbar_2014,Bordbar_2020}. This model computes emissivity for varying gas temperature, mixture composition, and path length using the HITEMP 2010 database \cite{Rothman_2010}. The $k_j$ and $a_j$ are then correlated to these results using polynomial fits summarized below. The model considers mixtures of gaseous \ce{CO2} and \ce{H2O}, the two most significant radiatively participating species in most combustion environments, using four gray gases and one clear gas. Absorption coefficients are calculated by
%
    \begin{linenomath}
        \begin{equation}
            \kappa_j=\sum_{k=0}^{4}d_{j,k}M_r^k,
        \end{equation}
    \end{linenomath}
%
    where $\kappa_j$ is the absorption coefficient for gray gas $j$, $d_{j,k}$ is a correlated model coefficient, and $M_r$ is the molar ratio $x_{\mathrm{H_2O}}/x_{\mathrm{CO_2}}$. The weight factors are calculated by
%
    \begin{linenomath}
        \begin{equation}
            a_j=\sum_{k=0}^{4}b_{j,k}T_r^k,
        \end{equation}
    \end{linenomath}
%
    where $a_j$ is the weighting factor for gas $j$, $b_{i,j}$ is computed as shown below,  and $T_r$ is a scaled temperature equal to $T/T_{ref}$ with $T_{ref}$=1200 K. The valid temperature range of the model is 300-2400 K; temperatures outside this range use the value at the respective bound. The value of $b_{i,j}$ is calculated by
%
    \begin{linenomath}
        \begin{equation}
            b_{j,k}=\sum_{i=0}^{4}C_{j,k,i}M_r^i,
        \end{equation}
    \end{linenomath}
%
    where $C_{j,k,i}$ is a correlated model coefficient. The model coefficients $d_{j,k}$ and $C_{j,k,i}$ are provided by Bordbar et~al. \citep{Bordbar_2014,Bordbar_2020} but updated values are used in RadLib.

    This particular WSGG model was chosen for RadLib for its performance, accuracy, and flexibility. Most WSGG models are limited to specific values of the molar \ce{H2O}--\ce{CO2} ratio, or to a limited range of values. This is true of Bordbar et al.'s 2014 model \cite{Bordbar_2014}, which used correlations valid for $0.01\le M_r\le4$. That paper summarizes a number of WSGG models and gives the applicable molar ratio range for several recent WSGG model versions.
    Bordbar et al.~\citep{Bordbar_2020} extended the molar ratio range to arbitrary values by interpolating $\kappa_j$ and $a_j$ between the pure component values and the corresponding limit on $M_r$ for values outside of the correlated range, and that is the model implemented here.

@@

    SLW and WSGG models are similar in that they approximate real gas mixtures with a set of radiatively gray gases, but differ in the way the gray gases are constructed. In traditional WSGG models, the component gases are only conceptually gray, and the absorption coefficients and weights are determined empirically \citep{Badger_2019}. In SLW approaches, however, the gases are gray in a given spectral band by construction. Rather than defining a gray gas $j$ by integrating over a band of sequential wavenumbers $\eta$ (which may have highly variable absorption coefficients), SLW models define a gray gas $j$ by integrating over a set of nonsequential wavenumbers that correspond to a given band of the absorption cross section $C_{\eta}$ with values constant to within the width of the band.

@@

    In the Planck Mean model, which treats a gas mixture as one gray gas, the soot absorption coefficient calculated from Eq.~\ref{e:soot2} is simply added to the gas absorption coefficient. Using the given values of $C_0$ and $C_2$ above, the expression for the soot absorption coefficient simplifies to  $\kappa_s=1817f_vT$ with units of \si{m^{-1}}.

@@

    These cases are intended to illustrate the use of the RadLib library and are not exhaustive. Details about these
    examples and their motivations can be found in their respective references. Comparison of these results to the
    LBL data, shown here, serve as model validation. For the WSGG and RCSLW models, direct comparison (not shown) of
    RadLib was
    made to examples presented in the model references with identical results (up to the resolution of the available
    data), which serves as verification of the implementation.

@@

\bibitem{Modest_2013}
M.~F. Modest, {Radiative Heat Transfer}, Third Edition, {Academic
Press}, New York, 2013.
